Practical Optional Types for Clojure

### 2015-05-20 formal-model.tex
add trivial structural rewrite rules for everything but java interop
revert to statically typed Java interop

\begin{figure}[t]
  \footnotesize
  $$
  \begin{altgrammar}
    \e{} &::=& \ldots \alt \reflectiveexpsyntax{} &\mbox{Expressions}\\
    \\

@@

    \classtableallsyntax{}
  \end{altgrammar}
  $$
  \begin{mathpar}
    {\TNew}

    {\TMethod}

@@

T-Field checks a resolved field expression by ensuring the target has
the correct static type, then returns a nilable type corresponding the Java type.

\begin{mathpar}
    {\TField}
\end{mathpar}

The rules T-Method and T-New work similarly (\figref{main:figure:javatyping}), varying
in the choice of nilability in the conversion function---methods
can return nil but constructors cannot. Void also does not have a constructor.

>>>>

\begin{figure}[t]
  \footnotesize
  $$
  \begin{altgrammar}
    \e{} &::=& \ldots   
            \alt \reflectiveexpsyntax{} &\mbox{Expressions}\\
     &\alt& \mininonreflectiveexpsyntax{}
    \\

@@

    \classtableallsyntax{}
  \end{altgrammar}
  $$
  \begin{mathpar}
    {\TNewStatic}

    {\TMethodStatic}

@@

T-FieldStatic checks a resolved field expression by ensuring the target has
the correct static type, then returns a nilable type corresponding the Java type.

\begin{mathpar}
    {\TFieldStatic}
\end{mathpar}

The rules T-MethodStatic and T-NewStatic work similarly (\figref{main:figure:javatyping}), varying
in the choice of nilability in the conversion function---methods
can return nil but constructors cannot. Void also does not have a constructor.
